--- 
title: Layers descriptions 
output: 
  html_document: 
    toc: true 
    toc_depth: 1 
    number_sections: false 
    toc_float: yes 
---

```{r, message=FALSE, echo=FALSE, warning=FALSE, error=FALSE} 
 library(tidyverse) 
 library(knitr) 
 
 layer_meta <- readr::read_csv('https://raw.githubusercontent.com/OHI-Science/whi/master/region2017/data_layers_table_wh.csv') 
 layer_path <- 'https://github.com/OHI-Science/whi/tree/master/region2017/layers_whi' 
 
 
```

 
# access to boat launch 
####[res_access_boat](https://github.com/OHI-Science/whi/tree/master/region2017/layers_whi/res_boat_access_whi2018.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/whi/master/region2017/conf/web/layers_all/access_to_boat_launch.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# access to shoreline 
####[res_shoreline_access](https://github.com/OHI-Science/whi/tree/master/region2017/layers_whi/res_shoreline_access_whi2018.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/whi/master/region2017/conf/web/layers_all/access_to_shoreline.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# annual participation in recreational activities 
####[r_participation](https://github.com/OHI-Science/whi/tree/master/region2017/layers_whi/rc_participation_whi2018.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/whi/master/region2017/conf/web/layers_all/annual_participation_in_recreational_activities.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# aquarium fishing 
####[fis_aquarium_catch](https://github.com/OHI-Science/whi/tree/master/region2017/layers_whi/fis_aquarium_catch_whi2018.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/whi/master/region2017/conf/web/layers_all/aquarium_fishing.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# area of active fishponds 
####[mar_fishpond_current](https://github.com/OHI-Science/whi/tree/master/region2017/layers_whi/mar_fishpond_current_whi2018.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/whi/master/region2017/conf/web/layers_all/area_of_active_fishponds.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# average daily visitor spending 
####[st_visitor_spending](https://github.com/OHI-Science/whi/tree/master/region2017/layers_whi/st_visitor_spending_whi2018.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/whi/master/region2017/conf/web/layers_all/average_daily_visitor_spending.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# beach condition 
####[hab_health_whi](https://github.com/OHI-Science/whi/tree/master/region2017/layers_whi/hab_health_whi2018.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/whi/master/region2017/conf/web/layers_all/beach_condition.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# beach extent 
####[hab_extent_whi](https://github.com/OHI-Science/whi/tree/master/region2017/layers_whi/hab_extent_whi2018.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/whi/master/region2017/conf/web/layers_all/beach_extent.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# beach trend 
####[hab_trend_whi](https://github.com/OHI-Science/whi/tree/master/region2017/layers_whi/hab_trend_whi2018.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/whi/master/region2017/conf/web/layers_all/beach_trend.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# bottom fisheries commercial catch 
####[fis_deep_catch](https://github.com/OHI-Science/whi/tree/master/region2017/layers_whi/fis_bottom_catch_whi2018.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/whi/master/region2017/conf/web/layers_all/bottom_fisheries_commercial_catch.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# coastal area 
####[lsp_area_1km_coast](https://github.com/OHI-Science/whi/tree/master/region2017/layers_whi/lsp_area_1km_coast_whi2018.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/whi/master/region2017/conf/web/layers_all/coastal_area.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# coastal wetland condition 
####[hab_health_whi](https://github.com/OHI-Science/whi/tree/master/region2017/layers_whi/hab_health_whi2018.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/whi/master/region2017/conf/web/layers_all/coastal_wetland_condition.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# coastal wetland extent 
####[hab_extent_whi](https://github.com/OHI-Science/whi/tree/master/region2017/layers_whi/hab_extent_whi2018.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/whi/master/region2017/conf/web/layers_all/coastal_wetland_extent.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# coastal wetland trend 
####[hab_trend_whi](https://github.com/OHI-Science/whi/tree/master/region2017/layers_whi/hab_trend_whi2018.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/whi/master/region2017/conf/web/layers_all/coastal_wetland_trend.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# commercial coastal pelagic fisheries catch 
####[fis_coast_pelagic_catch](https://github.com/OHI-Science/whi/tree/master/region2017/layers_whi/fis_cp_catch_whi2018.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/whi/master/region2017/conf/web/layers_all/commercial_coastal_pelagic_fisheries_catch.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# commercial reef fisheries catch 
####[fis_reef_catch](https://github.com/OHI-Science/whi/tree/master/region2017/layers_whi/fis_reef_catch_whi2018.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/whi/master/region2017/conf/web/layers_all/commercial_reef_fisheries_catch.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# commerical pelagic fisheries  catch 
####[fis_pelagic_catch](https://github.com/OHI-Science/whi/tree/master/region2017/layers_whi/fis_pelagic_catch_whi2018.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/whi/master/region2017/conf/web/layers_all/commerical_pelagic_fisheries__catch.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# conservation districts 
####[lsp_coastal_conservation](https://github.com/OHI-Science/whi/tree/master/region2017/layers_whi/lsp_coastal_conservation_whi2018.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/whi/master/region2017/conf/web/layers_all/conservation_districts.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# coral bleaching threat 
####[cc_sst_nearshore](https://github.com/OHI-Science/whi/tree/master/region2017/layers_whi/cc_sst_nearshore_whi2018.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/whi/master/region2017/conf/web/layers_all/coral_bleaching_threat.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# environmental protection 
####[t_env_sus](https://github.com/OHI-Science/whi/tree/master/region2017/layers_whi/t_env_sus_whi2018.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/whi/master/region2017/conf/web/layers_all/environmental_protection.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# ESA coastal plant status 
####[spp_ESA_status](https://github.com/OHI-Science/whi/tree/master/region2017/layers_whi/spp_ESA_status_whi2018.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/whi/master/region2017/conf/web/layers_all/ESA_coastal_plant_status.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# ESA marine mammal status 
####[spp_ESA_status](https://github.com/OHI-Science/whi/tree/master/region2017/layers_whi/spp_ESA_status_whi2018.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/whi/master/region2017/conf/web/layers_all/ESA_marine_mammal_status.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# ESA seabird and coastal bird status 
####[spp_ESA_status](https://github.com/OHI-Science/whi/tree/master/region2017/layers_whi/spp_ESA_status_whi2018.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/whi/master/region2017/conf/web/layers_all/ESA_seabird_and_coastal_bird_status.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# fishing households 
####[fishing_households](https://github.com/OHI-Science/whi/tree/master/region2017/layers_whi/fishing_households_whi2018.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/whi/master/region2017/conf/web/layers_all/fishing_households.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# fishpond status 
####[mar_fishpond_health](https://github.com/OHI-Science/whi/tree/master/region2017/layers_whi/mar_fishpond_health_whi2018.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/whi/master/region2017/conf/web/layers_all/fishpond_status.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# forest health 
####[hd_allien_veg](https://github.com/OHI-Science/whi/tree/master/region2017/layers_whi/hd_allien_veg_whi2018.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/whi/master/region2017/conf/web/layers_all/forest_health.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# habitat destruction from dredging 
####[hd_dredging](https://github.com/OHI-Science/whi/tree/master/region2017/layers_whi/hd_dredged_whi2018.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/whi/master/region2017/conf/web/layers_all/habitat_destruction_from_dredging.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# historical sites 
####[res_historical_sites](https://github.com/OHI-Science/whi/tree/master/region2017/layers_whi/res_historic_sites_whi2018.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/whi/master/region2017/conf/web/layers_all/historical_sites.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# land-based sediment export to nearshore water 
####[po_lbsp_sed](https://github.com/OHI-Science/whi/tree/master/region2017/layers_whi/po_lbsp_sed_whi2018.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/whi/master/region2017/conf/web/layers_all/land-based_sediment_export_to_nearshore_water.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# land-based source of pollution from agriculture and golf courses 
####[po_lbspaggolfrunoff](https://github.com/OHI-Science/whi/tree/master/region2017/layers_whi/po_lbspaggolfrunoff_whi2018.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/whi/master/region2017/conf/web/layers_all/land-based_source_of_pollution_from_agriculture_and_golf_courses.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# land-based source of pollution from urban runoff 
####[po_lbspurbanrunoff](https://github.com/OHI-Science/whi/tree/master/region2017/layers_whi/po_lbspurbanrunoff_mhi2017.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/whi/master/region2017/conf/web/layers_all/land-based_source_of_pollution_from_urban_runoff.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# land-based source of pollution nitrogen 
####[po_lbsp_nosds](https://github.com/OHI-Science/whi/tree/master/region2017/layers_whi/po_lbsp_nosds_whi2018.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/whi/master/region2017/conf/web/layers_all/land-based_source_of_pollution_nitrogen.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# mariculture risk 
####[mar_risk](https://github.com/OHI-Science/whi/tree/master/region2017/layers_whi/mar_risk_wh2018.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/whi/master/region2017/conf/web/layers_all/mariculture_risk.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# mariculture yield 
####[mar_harvest](https://github.com/OHI-Science/whi/tree/master/region2017/layers_whi/mar_harvest_whi2018.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/whi/master/region2017/conf/web/layers_all/mariculture_yield.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# monthly participation in recreational activities 
####[rc_participation](https://github.com/OHI-Science/whi/tree/master/region2017/layers_whi/r_participation_whi2018.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/whi/master/region2017/conf/web/layers_all/monthly_participation_in_recreational_activities.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# nearshore management areas 
####[lsp_mpa_3nm](https://github.com/OHI-Science/whi/tree/master/region2017/layers_whi/lsp_mpa_3nm_whi2018.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/whi/master/region2017/conf/web/layers_all/nearshore_management_areas.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# nearshore state waters 
####[lsp_area_3nm](https://github.com/OHI-Science/whi/tree/master/region2017/layers_whi/lsp_area_3nm_whi2018.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/whi/master/region2017/conf/web/layers_all/nearshore_state_waters.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# number of fishponds 
####[mar_fishpond_numbers](https://github.com/OHI-Science/whi/tree/master/region2017/layers_whi/mar_fishpond_numbers_whi2018.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/whi/master/region2017/conf/web/layers_all/number_of_fishponds.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# ocean and coastal jobs 
####[le_jobs](https://github.com/OHI-Science/whi/tree/master/region2017/layers_whi/le_jobs_whi2018.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/whi/master/region2017/conf/web/layers_all/ocean_and_coastal_jobs.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# ocean and coastal revenue 
####[le_gdp](https://github.com/OHI-Science/whi/tree/master/region2017/layers_whi/le_gdp_whi2018.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/whi/master/region2017/conf/web/layers_all/ocean_and_coastal_revenue.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# ocean and coastal sector mean wages 
####[le_wage](https://github.com/OHI-Science/whi/tree/master/region2017/layers_whi/le_wages_whi2018.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/whi/master/region2017/conf/web/layers_all/ocean_and_coastal_sector_mean_wages.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# operations 
####[mar_operations](https://github.com/OHI-Science/whi/tree/master/region2017/layers_whi/mar_operations_whi2018.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/whi/master/region2017/conf/web/layers_all/operations.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# reef condition 
####[hab_health_whi](https://github.com/OHI-Science/whi/tree/master/region2017/layers_whi/hab_health_whi2018.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/whi/master/region2017/conf/web/layers_all/reef_condition.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# reef extent 
####[hab_extent_whi](https://github.com/OHI-Science/whi/tree/master/region2017/layers_whi/hab_extent_whi2018.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/whi/master/region2017/conf/web/layers_all/reef_extent.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# reef fishing catch 
####[fp_reeffish_t](https://github.com/OHI-Science/whi/tree/master/region2017/layers_whi/fp_reeffish_t_whi2018.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/whi/master/region2017/conf/web/layers_all/reef_fishing_catch.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# reef trend 
####[hab_trend_whi](https://github.com/OHI-Science/whi/tree/master/region2017/layers_whi/hab_trend_whi2018.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/whi/master/region2017/conf/web/layers_all/reef_trend.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# resident sentiment 
####[t_sentiment](https://github.com/OHI-Science/whi/tree/master/region2017/layers_whi/t_sentiment_whi2018.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/whi/master/region2017/conf/web/layers_all/resident_sentiment.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# soft bottom condition 
####[hab_health_whi](https://github.com/OHI-Science/whi/tree/master/region2017/layers_whi/hab_health_whi2018.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/whi/master/region2017/conf/web/layers_all/soft_bottom_condition.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# soft bottom extent 
####[hab_extent_whi](https://github.com/OHI-Science/whi/tree/master/region2017/layers_whi/hab_extent_whi2018.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/whi/master/region2017/conf/web/layers_all/soft_bottom_extent.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# sustainability of bottomfish fishery 
####[fis_sus](https://github.com/OHI-Science/whi/tree/master/region2017/layers_whi/fis_sus_updated_whi2018.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/whi/master/region2017/conf/web/layers_all/sustainability_of_bottomfish_fishery.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# sustainability of pelagic fishery 
####[fis_sus](https://github.com/OHI-Science/whi/tree/master/region2017/layers_whi/fis_sus_updated_whi2018.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/whi/master/region2017/conf/web/layers_all/sustainability_of_pelagic_fishery.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# sustainability of reef fishery 
####[fis_sus](https://github.com/OHI-Science/whi/tree/master/region2017/layers_whi/fis_sus_updated_whi2018.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/whi/master/region2017/conf/web/layers_all/sustainability_of_reef_fishery.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# visitor arrivals 
####[t_visitor_arrivals](https://github.com/OHI-Science/whi/tree/master/region2017/layers_whi/t_visitor_arrivals_whi2018.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/whi/master/region2017/conf/web/layers_all/visitor_arrivals.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# visitor contributed GDP 
####[t_growth](https://github.com/OHI-Science/whi/tree/master/region2017/layers_whi/t_growth_whi2018.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/whi/master/region2017/conf/web/layers_all/visitor_contributed_GDP.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# watershed partnerships 
####[watershed_partnerships](https://github.com/OHI-Science/whi/tree/master/region2017/layers_whi/hab_watershed_partnerships_whi2018.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/whi/master/region2017/conf/web/layers_all/watershed_partnerships.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

 
# watersheds protected 
####[hd_watersheds](https://github.com/OHI-Science/whi/tree/master/region2017/layers_whi/hd_watersheds_whi2018.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                    x <- tempfile(fileext = 'Rmd')

                                    on.exit(unlink(x))

                                    download.file("https://raw.githubusercontent.com/OHI-Science/whi/master/region2017/conf/web/layers_all/watersheds_protected.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
